% Copyright (c) 2005 Nokia Corporation
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

\section{\module{camera} ---
    Interface for taking photographs}

\declaremodule{extension}{camera}
\label{sec:camera}

\begin{notice}[note]
Not available for S60 1st Edition.
\end{notice}

The \module{camera} module enables taking photographs. 

The \module{camera} module has the following functions\footnote{ 
Descriptions for some of the values are based on information found in S60 SDK documentation \cite{S60Doc}}:

\begin{funcdesc}{cameras_available}{}
Returns the number of cameras available in the device.
\end{funcdesc}

\begin{funcdesc}{image_modes}{}
Returns the image modes supported in the device as a list of strings, for 
example: \code{['RGB12', 'RGB', 'RGB16'].}
\end{funcdesc}

\begin{funcdesc}{image_sizes}{}
Returns the image sizes (resolution) supported in the device as a list of 
\code{(x, y)} tuples, for example: \code{[(640, 480), (160, 120)]}.
\end{funcdesc}

\begin{funcdesc}{flash_modes}{}
Returns the flash modes available in the device as a list of strings. 
\end{funcdesc}

\begin{funcdesc}{max_zoom}{}
Returns the maximum digital zoom value supported in the device as an 
integer. 
\end{funcdesc}

\begin{funcdesc}{exposure_modes}{}
Returns the exposure settings supported in the device as a list of strings. 
\end{funcdesc}

\begin{funcdesc}{white_balance_modes}{}
Returns the white balance modes available in the device as a list of 
strings. 
\end{funcdesc}

\begin{funcdesc}{take_photo}{\optional{mode, size, flash, zoom, exposure, white_balance, position}}
Takes a photograph and returns the image in \code{Image} format (for more 
information on \code{Image} format, see Chapter \ref{sec:graphics} 
\refmodule{graphics} Module). If some other application is using the camera, 
this operation fails, for example with \code{SymbianError: KErrInUse}. The 
settings listed below describe all settings that are supported by the 
\code{camera} module. You can retrieve the mode settings available for your 
device by using the appropriate functions listed at the beginning of this 
chapter.

\begin{itemize}
\item \var{mode} is the display mode of the image. The default value is \code{'RGB16'}. The following display modes are supported:
	\begin{itemize}
	\item \code{'RGB12'}: 4096 colors (12 bits per pixel)
	\item \code{'RGB16'}: 65536 colors (16 bits per pixel). Default value, always supported
	\item \code{'RGB'}: 16.7 million colors (24 bits per pixel)
	\end{itemize}
\item \var{size} is the resolution of the image. The default value is \code{(640, 480)}. The following sizes are supported, for example, in Nokia 6630: \code{(1280, 960)}, \code{(640, 480)} and \code{(160, 120)}.
\item \var{flash} is the flash mode setting. The default value is \code{'none'}. The following flash mode settings are supported:
	\begin{itemize}
	\item \code{'none' \newline
}No flash. Default value, always supported
	\item \code{'auto' \newline
}Flash will automatically fire when required
	\item \code{'forced' \newline
}Flash will always fire
	\item \code{'fill_in' \newline
}Reduced flash for general lighting
	\item \code{'red_eye_reduce' \newline
}Red-eye reduction mode
	\end{itemize}
\item \var{zoom} is the digital zoom factor. It is assumed to be on a linear scale from 0 to the maximum zoom value allowed in the device. The default value is \code{0}, meaning that zoom is not used. 
\item \var{exposure} is the exposure adjustment of the device. Exposure is a combination of lens aperture and shutter speed used in taking a photograph. The default value is \code{'auto'.} The following exposure modes are supported:
	\begin{itemize}
	\item \code{'auto'} \newline
Sets exposure automatically. Default value, always supported
	\item \code{'night'} \newline
Night-time setting for long exposures
	\item \code{'backlight' } \newline
Backlight setting for bright backgrounds
	\item \code{'center'} \newline
Centered mode for ignoring surroundings
	\end{itemize}
\item \var{white_balance} can be used to adjust white balance to match the main source of light. The term white balance refers to the color temperature of the current light. A digital camera requires a reference point to represent white. It will then calculate all the other colors based on this white point. The default value for \var{white_balance} is \code{'auto'} and the following white balance modes are supported:
	\begin{itemize}
	\item \code{'auto'} \newline
Sets white balance automatically. Default value, always supported
	\item \code{'daylight'} \newline
Sets white balance to normal daylight
	\item \code{'cloudy}' \newline
Sets white balance to overcast daylight
	\item \code{'tungsten'} \newline
Sets white balance to tungsten filament lighting
	\item \code{'fluorescent}' \newline
Sets white balance to fluorescent tube lighting
	\item \code{'flash'} \newline
Sets white balance to flash lighting
	\end{itemize}
\item \var{position} is the camera used if the device, such as Nokia 6680, has several cameras. In Nokia 6680, the camera pointing to the user of the device is located in position \code{1}, whereas the one pointing away from the user is located in position \code{0}. The default \var{position} is \code{0}.
\end{itemize}
\end{funcdesc}
