% Copyright (c) 2005 Nokia Corporation
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

\section{Support for Python Standard Library}
\label{sec:standard}

The standard library support in Python for S60 is summarized in Table 
\ref{standardsupport}. For API descriptions, see \cite{PyLibRef}.

\begin{center}
\begin{longtable}{|l|l|l|p{200pt}|}
\hline
{\bf Name}& 
{\bf Type}& 
{\bf Status}& 
{\bf Remarks} \\
\hline
\code{{\_}testcapi}& 
PYD& 
Y& 
 \\
\hline
\code{anydbm}& 
PY& 
X& 
DBM API is implemented by PY \code{e32dbm} that relies on PYD \code{e32db} (see Chapter \ref{sec:e32dbm}, e32dbm Module) \\
\hline
\code{atexit}& 
PY& 
X& 
 \\
\hline
\code{base64}& 
PY& 
X& 
 \\
\hline
\code{bdb}& 
PY& 
(X)& 
 \\
\hline
\code{binascii}& 
built-in& 
X& 
 \\
\hline
\code{cmd}& 
PY& 
(X)& 
 \\
\hline
\code{code}& 
PY& 
X& 
 \\
\hline
\code{codecs}& 
PY& 
X& 
 \\
\hline
\code{codeop}& 
PY& 
X& 
 \\
\hline
\code{copy}& 
PY& 
X& 
 \\
\hline
\code{copy{\_}reg}& 
PY& 
X& 
 \\
\hline
\code{cStringIO}& 
built-in& 
X& 
 \\
\hline
\code{dis}& 
PY& 
(X)& 
 \\
\hline
\code{errno}& 
built-in& 
X& 
 \\
\hline
\code{exceptions}& 
built-in& 
X& 
 \\
\hline
\code{{\_}{\_}future{\_}{\_}}& 
PY& 
X& 
 \\
\hline
\code{httplib}& 
PY& 
X& 
 \\
\hline
\code{imp}& 
built-in& 
X& 
 \\
\hline
\code{keyword}& 
PY& 
X& 
 \\
\hline
\code{linecache}& 
PY& 
X& 
 \\
\hline
\code{marshal}& 
built-in& 
X& 
 \\
\hline
\code{math}& 
built-in& 
X& 
 \\
\hline
\code{md5}\footnote{Derived from the RSA Data Security, Inc. MD5 Message-Digest Algorithm.}& 
built-in& 
X& 
 \\
\hline
\code{mimetools}& 
PY& 
X& 
 \\
\hline
\code{operator}& 
built-in& 
X& 
 \\
\hline
\code{os, os.path}& 
PY& 
X& 
Wraps built-in \code{e32posix}. Limitations discussed in Section \ref{subsec:limitations}, Limitations and Areas of Development. \\
\hline
\code{pdb}& 
PY& 
(X)& 
 \\
\hline
\code{quopri}& 
PY& 
X& 
 \\
\hline
Name& 
Type& 
Status& 
Remarks \\
\hline
\code{random}& 
PY& 
X& 
 \\
\hline
\code{re}& 
PY& 
X& 
Uses PY \code{sre} as its engine. \\
\hline
\code{repr}& 
PY& 
X& 
 \\
\hline
\code{rfc822}& 
PY& 
X& 
 \\
\hline
\code{select}& 
PY& 
X& 
A minimal implementation: \code{select} is supported only for input from sockets. \\
\hline
\code{socket}& 
PY& 
X& 
Requires PYD \code{e32socket}. Contains extensions as described in Section \ref{subsec:socket}, socket Module. Limitations discussed in Section \ref{subsec:limitations}, Limitations and Areas of Development.  \\
\hline
\code{sre}& 
PY& 
X& 
Wraps built-in \code{{\_}sre}. \\
\hline
\code{string}& 
PY& 
X& 
 \\
\hline
\code{StringIO}& 
PY& 
X& 
 \\
\hline
\code{struct}& 
built-in& 
X& 
 \\
\hline
\code{sys}& 
built-in& 
X& 
 \\
\hline
\code{thread}& 
built-in& 
X& 
Contains extensions as described in Section \ref{subsec:thread}, thread Module \\
\hline
\code{threading}& 
PY& 
(X)& 
 \\
\hline
\code{time}& 
built-in& 
X& 
 \\
\hline
\code{traceback}& 
PY& 
X& 
 \\
\hline
\code{types}& 
PY& 
X& 
 \\
\hline
\code{urllib}& 
PY& 
X& 
 \\
\hline
\code{urlparse}(urlsplit only)& 
PY& 
X& 
 \\
\hline
\code{uu}& 
PY& 
X& 
 \\
\hline
\code{warnings}& 
PY& 
X& 
 \\
\hline
\code{whichdb}& 
PY& 
X& 
 \\
\hline
\code{xreadlines}& 
built-in& 
X& 
 \\
\hline
\code{zipfile}& 
PY& 
X& 
 \\
\hline
\code{zlib}& 
PYD& 
X& 
 \\
\hline
\caption{Status of library module support.}
\label{standardsupport}
\end{longtable}
\end{center}

Table \ref{standardsupport} uses the following coding for module types:

\begin{itemize}
\item PY -- module is implemented in Python.
\item Built-in -- module is a built-in C/C++ module.
\item PYD -- module is a dynamically loadable C/C++ module.
\end{itemize}
For support status, the following codes are used:

\begin{enumerate}
\item[\textbullet] X -- included to the Series 60 Python distribution.
\item[\textbullet] (X) -- not included to the Series 60 Python distribution, but works both on phone and SDK.
\item[\textbullet] Y -- included only to the SDK distribution.
\end{enumerate}
